{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

        \subsection{GMAPG main algorithm}
            % GMAPG ------------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function GMAPG Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                            $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
                            $x_{-1}$ & Vector\\
                            $L\in \RR$ & $L > 0$\\ 
                            $r $ & $r \in (0, 1)$ \\ 
                            $\rho \in \RR$ & $\rho \in (0, 1)$ \\
                            $N_{\min}\in \N$ & $N \ge 1$ \\
                            $N \in \N$ & $N \ge N_{\min}$ \\
                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 
                        \end{tabular}
                    }
                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = L_0(x_0 - y_0).$}
                    \FOR{$k := 1, 2,\ldots, N$}
                        \STATE{\noindent
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                        }
                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                        \STATE{\noindent
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        }
                        \STATE{$G_k:= L_k(\tilde x_k - y_k)$}
                        \STATE{\noindent
                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        }
                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                            \STATE{\textbf{break}}
                        \ENDIF
                    \ENDFOR
                    \STATE{\textbf{Return: }$x_k, k, \overline L$}
                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
                \end{algorithmic}
            \end{algorithm}
            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
            For example, we chose $r= 0.4, \rho = 2^{1/1024}$.

@@

@@

            \STATE{$n_0 := 0$.}

@@

                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1} := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

@@

        We make the rule that $z_{j + 1, -1} = z_{j, p_j}$ for compatibility of the theorems in the previous sections. 
        For example in line 7 at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate of the inner loop and, it's assigned to $z_{j + 1}$ by the outer loop. 
        In that case we denote $z_{j + 1, -1}$ as the initial iterate pass into the inner loop for the $j + 1$ iteration, and $z_{j, p_j}$ would denote the last iteration before exiting the inner loop for the $j$ th iteration of the outer loop. 
        Therefore, $z_{j + 1, -1} = z_{j, p_j}$ and all iterates generated by the inner loop is the finite sequence $(z_{j, k})_{k = 0}^{p_j}$. 

@@

        \begin{lemma}[maximum iteration needed for an optimality gap ratio]\label{lemma:prog-ratio}
            Denote $F^+ := \inf_xF(x)$ and, let $X^+$ denotes the set of minimizers. 

@@

        \begin{lemma}[bounds on inner iteration counts]

@@

        \end{proof}
        \begin{lemma}[bounds on outer iteration counts]
            ...
        \end{lemma}

>>>>

        \subsection{GMAPG main algorithm}
            % GMAPG ------------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function GMAPG Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                            $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
                            $x_{-1}$ & Vector\\
                            $L\in \RR$ & $L > 0$\\ 
                            $r $ & $r \in (0, 1)$ \\ 
                            $\rho \in \RR$ & $\rho \in (0, 1)$ \\
                            $N_{\min}\in \N$ & $N \ge 1$ \\
                            $N \in \N$ & $N \ge N_{\min}$ \\
                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 
                        \end{tabular}
                    }
                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = L_0(x_0 - y_0).$}
                    \FOR{$k := 1, 2,\ldots, N$}
                        \STATE{\noindent
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                        }
                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                        \STATE{\noindent
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        }
                        \STATE{$G_k:= L_k(\tilde x_k - y_k)$}
                        \STATE{\noindent
                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        }
                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                            \STATE{\textbf{break}}
                        \ENDIF
                    \ENDFOR
                    \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
                \end{algorithmic}
            \end{algorithm}
            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
            For example, we chose $r= 0.4, \rho = 2^{1/1024}$.

@@

        \begin{align}\label{ineq:rgmapg-exit-cond}

@@

            \STATE{$n_0 := 0; z_0 = x_{-1}$.}

@@

                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G_k^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

                \IF{$M \le 0 \textbf{ or } G_k^+ \le \epsilon$}

@@

        We make the choice to have $z_{j + 1, -1} = z_{j, p_j} = z_{j + 1}$ for consistencies across theorems from previous sections. 
        For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. Denote $x_{p_j}$ as $z_{j, p_j}$ and, it's assigned to $z_{j + 1}$ by the outer loop so $x_{p_j} = z_{j, p_j} = z_{j + 1}$. 
        It continues and $z_{j + 1}$ will be the initial iterate pass into the inner loop for the $j + 1$ iteration, and hence $z_{j + 1} =z_{j + 1, -1}$. 

@@

        \begin{lemma}[maximum iteration needed for an optimality gap ratio]\;\label{lemma:prog-ratio}\\
            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$ and, $X^+$ is the set of minimizers. 

@@

        \begin{lemma}[inner iteration is bounded above]\label{lemma:rgmapg-inner-bnds}
            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$ and, $X^+$ is the set of minimizers. 
            Consider any $j \ge 1$ iteration experienced by the outer loop. 
            Let $(z_{j,k})_{k\ge 0}^{p_{j}}$ be the sequence generated by Algorithm \ref{alg:linear-rgmapg} in the $j$ th iteration of outer loop. 
            Define $\bar p := \frac{4\sqrt{2L(1 + e)}}{\sqrt{\mu}}$, then $p_{j} \le \bar p$. 
            The end result is constructed upon the following intermediate results that are proved at the end: 
                \item [(i)] If $k \ge \bar p$, then exit condition $\mathbf E_{\chi}^a$ is true hence $p_j \le \max(\bar p, n_j)$ for all $j \ge 0$. 
                \item [(ii)] If $p_{j - 1} \le p_j\le \bar p$  then $n_{j + 1} \le \bar p$. 
            Take note that $n_0 = 0, n_1 = p_0$ hence (i) gives $p_0 \le \bar p$, and $p_1 \le \max(\bar p, n_1) = \max(\bar p, p_0) \le \bar p$. 
            We now have the base case: $p_0 \le p_1 \le \bar p$. 
            Inductively assume $p_{j - 1} \le p_j \le \bar p$ then: 
                p_{j + 1} \underset{\text{(i)}}{\le} \max(\bar p, n_{j + 1}) \underset{\text{(ii)}}{\le} \bar p. 
            Therefore, for all $j \ge 0$, $p_j \le \bar p$. 
            \textbf{Proof of (i)}. 
            Recall exit condition in \eqref{ineq:rgmapg-exit-cond} has $m = \lfloor k/2\rfloor + 1$. 
            Starting with the statement hypothesis it has $k \ge \ bar p$ therefore: 
                0 &\le k/2 - \bar p/2 \le \lfloor k/2\rfloor + 1 - \bar p/2
                = m - \bar p /2 \le m - \lfloor \bar p/2\rfloor
                &= m - \left\lfloor 
                    \frac{2\sqrt{2L(1 + e)}}{\sqrt{\mu}}
                \right\rfloor \le 
                m - \left\lfloor 
                    \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}}
                \right\rfloor
            On the last inequality we used Proposition \ref{prop:bnded-lip-ls} which has $\widehat L_k \le 2 L$. 
            Observe that the inequality allow us to apply Lemma \ref{lemma:prog-ratio} with $m = k$ which yields: 
                e^{-1} \ge \frac{F(z_{j, m}) - F^+}{F(z_{j, -1}) - F(z_{j, m})} \ge \frac{F(z_{j, m}) - F(z_{j, k})}{F(z_{j, -1}) - F(z_{j, m})} \implies \mathbf E_{\chi}^a. 
            Observe that line 11 of Algorithm \ref{alg:gmapg} exits as soon as possible if $E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore $p_j \le \max(\bar p, n_j)$. 
            \textbf{Proof of (ii)}. 
            Inductively assume that $p_{j - 1} \le p_j \le \bar p$. 
            If $p_{j - 1} \le \bar p /2$ then Line 14, 16 implies that $n_{j} \le \max(p_{j - 1}, 2p_{j - 1}) \le \bar p$. 
            Otherwise, $p_{j - 1} > \bar p/2$, and using Proposition \ref{prop:bnded-lip-ls} it means 
                p_{j - 1} \ge \bar p /2 = \frac{2\sqrt{2L(1 + e)}}{\sqrt{\mu}} \ge \left \lfloor \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}} \right\rfloor. 
            The above inequality allows us to use Lemma \ref{lemma:prog-ratio} which yields 
                e^{-1} \ge \frac{F(z_{j - 1, p_{j - 1}}) - F^+}
                {F(z_{j - 1, -1}) - F(z_{j - 1, p_{j - 1}})}
                \ge 
                \frac{F(z_j) - F(z_{j + 1})}
                {F(z_{j - 1}) - F(z_{j})} \implies n_{j + 1} = p_{j + 1}.
            Therefore, there is no doubling at line 14 of Algorithm \ref{alg:linear-rgmapg}, hence $n_{j + 1} \le \bar p$ still. 
        We just show that the sequence $n_j$ is bounded above, and it must have a limit because it's also monotone increasing, which implies that at some point, the doubling of $n_{j + 1} = 2p_j$ must stop for the outer loop. 
        The following lemma shows that when that happens, the algorithm will always terminate after a finite number of iterations of the outer loop. 
        \begin{lemma}[bounds on outer iteration counts]

@@
